Descriptive, not injunctive, social norms caused increases in mask wearing during the COVID-19 pandemic

### 2022-12-19 appendix.Rmd
submission

---
output:
  pdf_document: default
  html_document: default
---
\renewcommand{\appendixname}{\textbf{Supplementary Materials}}
\renewcommand{\thefigure}{S\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{S\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{S\arabic{table}} \setcounter{equation}{0}

@@

(ref:plotCorBehNormCaption) _Predictions from multilevel models with self-reported mask wearing behavior as the outcome variable and (a) perceived strength of descriptive norms and (b) perceived strength of injunctive norms as independent predictor variables._ Models contain random intercepts for participants and time points. Lines are fixed effect regression lines from multilevel models, shaded areas are 95% confidence intervals.

@@

(ref:plotCDCSensCaption) _Predictions from multilevel models with change points in line with changes in CDC mask wearing recommendations._ These models track temporal changes in (a) self-reported mask wearing behavior, (b) perceived strength of descriptive norms, and (c) perceived strength of injunctive norms. Time is included as a continuous linear predictor, scaled between 0 and 1, with three forced change points (dashed lines). From the left, the first dashed line indicates when the CDC relaxed their mask wearing recommendations in March 2021, the second dashed line indicates when the CDC strengthened their mask wearing recommendations in July 2021, and the third dashed line indicates when the CDC updated their community levels and relaxed their mask wearing recommendations in March 2022. This results in the estimation of five fixed effect parameters: the initial intercept, the slope in the first window, the slope in the second window, the slope in the third window, and the slope is the fourth window. Bolded lines and shaded areas represent fixed effect regression lines from multilevel models and 95% confidence intervals, respectively.

@@

(ref:plotDAGCaption) _Directed acyclic graph reflecting causal assumptions._ In this model, a general unobserved sensitivity to social norms (NormSens) causes perceptions of descriptive social norms (DesNorm) and perceptions of injunctive social norms (InjNorm), and perceptions of descriptive and injunctive norms directly cause mask wearing behavior (Mask). Perceptions of descriptive and injunctive norms also indirectly cause mask wearing behavior through non-social beliefs, specifically factual beliefs (Fact) and personal normative beliefs (PersNorm). Finally, political orientation (PolOri) is an exogenous variable that is a common cause of all other variables. Using the backdoor criterion (Pearl, 1995), this causal model implies that it is necessary to control for perceptions of injunctive norms, factual beliefs, personal normative beliefs, and political orientation to estimate the direct causal effect of perceived descriptive norms on mask wearing. Similarly, it is necessary to control for perceptions of descriptive norms, factual beliefs, personal normative beliefs, and political orientation to estimate the direct causal effect of perceived injunctive norms on mask wearing.

@@

```{r changePointsTable, echo=F, warning=F, message=F}
apa_table(
  changePointsTable,
  booktabs = TRUE,
  longtable = TRUE,
  align = c("l", "c", "c", "c"),
  caption = "(ref:changePointsTableCaption)"
)
```

@@

```{r itemTable, echo=F, warning=F, message=F}
apa_table(
  itemTable,
  booktabs = TRUE,
  longtable = TRUE,
  #align = c("m{2.5cm}", "m{2.5cm}", "m{9cm}"),
  caption = "(ref:itemTableCaption)"
)
```

>>>>

---
output:
  pdf_document: default
  html_document: default
---
\renewcommand{\appendixname}{\textbf{Supplementary Material}}
\renewcommand{\thefigure}{S\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{S\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{S\arabic{table}} \setcounter{equation}{0}

@@

(ref:plotDAGCaption) _Directed acyclic graph reflecting causal assumptions._ In this model, a general unobserved sensitivity to social norms (NormSens) causes perceptions of descriptive social norms (DesNorm) and perceptions of injunctive social norms (InjNorm), and perceptions of descriptive and injunctive norms directly cause mask wearing (Mask). Perceptions of descriptive and injunctive norms also indirectly cause mask wearing through non-social beliefs, specifically factual beliefs (Fact) and personal normative beliefs (PersNorm). Finally, political orientation (PolOri) is an exogenous variable that is a common cause of all other variables. Using the backdoor criterion (Pearl, 1995), this causal model implies that it is necessary to control for perceptions of injunctive norms, factual beliefs, personal normative beliefs, and political orientation to estimate the direct causal effect of perceived descriptive norms on mask wearing. Similarly, it is necessary to control for perceptions of descriptive norms, factual beliefs, personal normative beliefs, and political orientation to estimate the direct causal effect of perceived injunctive norms on mask wearing.

(ref:plotCorBehNormCaption) _Predictions from multilevel models with self-reported mask wearing as the outcome variable and (a) perceived strength of descriptive norms and (b) perceived strength of injunctive norms as independent predictor variables._ Models contain random intercepts for participants and time points. Lines are fixed effect regression lines from multilevel models, shaded areas are 95% confidence intervals.

@@

(ref:plotCDCSensCaption) _Predictions from multilevel models with change points in line with changes in CDC mask wearing recommendations._ These models track temporal changes in (a) self-reported mask wearing, (b) perceived strength of descriptive norms, and (c) perceived strength of injunctive norms. Time is included as a continuous linear predictor, scaled between 0 and 1, with three forced change points (dashed lines). From the left, the first dashed line indicates when the CDC relaxed their mask wearing recommendations in March 2021, the second dashed line indicates when the CDC strengthened their mask wearing recommendations in July 2021, and the third dashed line indicates when the CDC updated their community levels and relaxed their mask wearing recommendations in March 2022. This results in the estimation of five fixed effect parameters: the initial intercept, the slope in the first window, the slope in the second window, the slope in the third window, and the slope is the fourth window. Bolded lines and shaded areas represent fixed effect regression lines from multilevel models and 95% confidence intervals, respectively.

@@

@@

```{r changePointsTable, echo=F, warning=F, message=F}
apa_table(
  changePointsTable,
  booktabs = TRUE,
  longtable = TRUE,
  font_size = "small",
  align = c("l", "c", "c", "c"),
  caption = "(ref:changePointsTableCaption)"
)
```

@@

```{r itemTable, echo=F, warning=F, message=F}
apa_table(
  itemTable,
  booktabs = TRUE,
  longtable = TRUE,
  align = c("m{2.5cm}", "m{2.5cm}", "m{9cm}"),
  caption = "(ref:itemTableCaption)"
)
```
